Single Cell Xenopus TMT Analysis

### 2020-03-03 Untitled.Rmd
update

## Setup
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RColorBrewer)
library(pheatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
```

@@

rbind(glyc2,tibble(GO = "All",
      cor = cor[lower.tri(cor)])) %>%
  ggplot(., aes(x = cor, fill = GO, alpha = 0.75)) + geom_density() +
  geom_rug(data = glyc2)

# pathview(genes, 
#          pathway.id = pathway, 
#          species = 'mmu', 
#          same.layer = F,
#          low = list(gene = 'blue'),
#          mid = list(gene = 'transparent'),
#          high = list(gene = 'red'),
#          limit = list(gene = c(-2,2))
# )

>>>>

## Setup
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RColorBrewer)
library(pheatmap)
library(GGally)
library(VIM)
library(org.Xl.eg.db)
library(GO.db)
library(ggrepel)
library(plotly)
library(cowplot)
library(patchwork)
```

@@

p1 <- rbind(glyc2,tibble(GO = "All",
      cor = cor[lower.tri(cor)])) %>%
  ggplot(.,aes(x = cor, fill = GO)) + geom_density(alpha = 0.75, color = "transparent") +
  scale_fill_manual(values = c('#bababa','#e08214')) +
  geom_rug(data = glyc2, color = '#e08214') +
  theme_bw() +
  #theme(legend.position = c(.2,.8)) +
  theme(legend.position = "none") +
  xlim(-1,1)

p2 <- rbind(glyc2,tibble(GO = "All",
      cor = cor[lower.tri(cor)])) %>%
  ggplot(., aes(x = GO, y = cor, fill = GO)) + 
  geom_boxplot(notch = TRUE, alpha = 0.75) +
  scale_fill_manual(values = c('#bababa','#e08214')) +
  theme_bw() +
  theme(legend.position = "bottom") +
  ylim(-1,1) +
  coord_flip()

plot_grid(p1,p2, ncol = 1, 
          rel_heights = c(2,1),
          align = 'v')

p1/p2 + 
  plot_annotation(title = "Glycolysis",
                  tag_levels = "A") +
  plot_layout(heights = c(2,1))

# pathview(genes, 
#          pathway.id = pathway, 
#          species = 'mmu', 
#          same.layer = F,
#          low = list(gene = 'blue'),
#          mid = list(gene = 'transparent'),
#          high = list(gene = 'red'),
#          limit = list(gene = c(-2,2))
# )
  p1
```

## Figure 1
```{r fig.height=6.5, fig.width=6.5}
set.seed(41)

low_cor <- corProts(2, 100, 0, 100, 30)
low_cor <- low_cor %>% as_tibble() %>% mutate(cor = "low_cor", time = 1:nrow(low_cor)) %>%
  rename(ProtA = "V1", ProtB = "V2")

high_cor <- corProts(2, 100, 0.8, 100, 30)
high_cor <- high_cor %>% as_tibble() %>% mutate(cor = "high_cor", time = 1:nrow(high_cor)) %>%
  rename(ProtA = "V1", ProtB = "V2")

p1 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = time, y = abundance, color = protein)) + geom_path() +
  facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

p2 <- rbind(low_cor, high_cor) %>% pivot_longer(ProtA:ProtB, names_to = "protein", values_to = "abundance") %>%
  ggplot(., aes(x = protein, y = abundance, color = protein)) + 
  geom_boxplot() + facet_wrap(~cor, ncol = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")

p3 <- rbind(low_cor, high_cor) %>%
  ggplot(., aes(x = ProtA, y = ProtB, color = cor)) + geom_point() +
  stat_ellipse() +
  theme_minimal() +
  theme(legend.position = "bottom")

p4 <- tibble(cor = c("High Cor","Low Cor"),
       var_sum = c(sqrt(30^2 + 30^2 + 2*0.8*30^2),
                   sqrt(30^2 + 30^2 + 2*0*30^2))) %>%
  ggplot(., aes(x = cor, y = var_sum, fill = cor)) + geom_bar(stat = "identity") +
  theme_minimal()

# pp1 <- p1 + p2 + plot_layout(widths = c(3,1))
# pp2 <- p3 + p4
# 
# pp1 / pp2 + plot_annotation(tag_levels = "A") & theme(legend.position = "none")

p1 / (p3 + p4) + plot_annotation(tag_levels = "A") & theme(legend.position = "none")
